Glyph-maps for Visualizing Climate Data and Models

### 2012-06-21 cover-letter.tex
made pdf image for publishers

Please find attached our submission for the special issue of Environmetrics on Climate. The title is Glyph-maps for Visualizing Climate Data and Models, with authors Hadley Wickham, Heike Hofmann, Charlotte Wickham and myself. We hope that you find this paper interesting reading, and that it will make a valuable contribution  to the special issue.

>>>>

Please find attached our submission for the special issue of Environmetrics on Climate. The title is Glyph-maps for Visually Exploring Temporal Patterns in Climate Data and Models, with authors Hadley Wickham, Heike Hofmann, Charlotte Wickham and myself. We hope that you find this paper interesting reading, and that it will make a valuable contribution  to the special issue.
